Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-02-01 ms.tex
I added a figure showing that the IDL and python Mie scattering are in excellent agreement.

>>>>

\clearpage
\pagebreak
\subsection{Mie scattering}

My old Mie scattering code was in IDL and would be more work to incorporate into MCMC fitting, so I found python package \texttt{miescatter} and did a comparison with my IDL code.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{python_vs_IDL_example.pdf}
\caption{Example Mie scattering extinction cross sections $Q_{ext}$ for a spherical particle with a radius of 0.5~$\mu$m and a complex index of refraction of n=1.825 - 0.001 $i$. The IDL and python code's are in excellent agreement.}\label{fig:IDLvsPython}
\end{centering}
\end{figure}
